A Tale of Two Dictionary Learning Problems

### 2020-08-06 manuscripts/thesis/introduction.tex
new intro

For many signal analysis tasks, however, no one basis can convey clearly all of the relevant information in the signal. For instance, if a signal can be either a sine wave or a delta function, then neither the standard basis nor the Fourier basis will indicate one case as explicitly as it does the other. 
The need for such freedom of expression led to the development of redundant signal representations utilizing overcomplete dictionaries, which consist of more atoms than there are dimensions of the signal. An overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent atoms, and the intention is to seek the optimal such representation as measured by some task-specific cost function.

>>>>

For many signal analysis tasks, however, no one basis can convey clearly all of the relevant information in the signal. For instance, if a signal can be either a sine wave or a delta function, then neither the standard basis nor the Fourier basis will indicate one case as explicitly as it does the other. 
The need for such freedom of expression led to the development of redundant signal representations utilizing overcomplete dictionaries, which consist of more atoms than there are dimensions of the signal. An overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent atoms. The intention is then to seek the best such representation, be it by some analytic criteria, or as measured by some task-specific cost function.
